Wu-Tang Clan

### 2015-03-20 rmtw/a6/latex8.tex
sadasd
sad

\author{\textsuperscript{*}John Burchell \qquad \textsuperscript{x}William Granli \\
		\textsuperscript{*}john.a.burchell@gmail.com \qquad \textsuperscript{x}william.granli@gmail.com \\
		\textsuperscript{*x}Software Engineering \& Management  \\
		\textsuperscript{*x}University of Gothenburg }

@@

%Structure of the paper
The sections following the Introduction are structured as follows: In Section II, we present a literature review on research related to our study. Section II describes the case company and how it was selected. A description of our methodology is introduced in Section III.

>>>>

% \author{\textsuperscript{*}John Burchell \qquad \textsuperscript{x}William Granli \\
% 		\textsuperscript{*}john.a.burchell@gmail.com \qquad \textsuperscript{x}william.granli@gmail.com \\
% 		\textsuperscript{*x} Computer Science and Engineering  \\
% 		\textsuperscript{*x}University of Gothenburg }
\author{John Burchell \qquad William Granli \\
		john.a.burchell@gmail.com \qquad william.granli@gmail.com \\
		Computer Science and Engineering  \\
		University of Gothenburg }

@@

%Structure of the paper
The sections following the Introduction are structured as follows: In Section 2, we present a literature review on research related to our study. Section 3 describes the case company and how it was selected. A description of our methodology is introduced in Section 4.
